Balance responses in MS

### 2020-02-04 R/msBalance.Rmd
added labels to normalization figure

***
```{r rawEMG, out.width = "100%", fig.align = "left", fig.cap = captionRawEmg}
p = ggplot(taR, aes(x = Time, y = V)) + geom_line(aes(color = Participant), show.legend = FALSE, alpha = 0.5) + facet_grid(Group ~ `Perturbation Direction`) + theme_minimal_grid() +
  geom_jitter(mapping = aes(x = 0, y = Vm, color = Participant), data = taRNorm %>% left_join(participants %>% select(Participant, Group)), show.legend = FALSE, height = 0, width = 0.01)
p
```

>>>>

***
```{r rawEMG, out.width = "100%", fig.align = "left", fig.cap = captionRawEmg}
# p = ggplot(taR, aes(x = Time, y = V)) + geom_line(aes(color = Participant), show.legend = FALSE, alpha = 0.5) + facet_grid(Group ~ `Perturbation Direction`) + theme_minimal_grid() +
#   geom_jitter(mapping = aes(x = 0, y = Vm, color = Participant), data = taRNorm %>% left_join(participants %>% select(Participant, Group)), show.legend = FALSE, height = 0, width = 0.01)
# p
p = ggplot(taR, aes(x = Time, y = V)) + geom_line(aes(color = Participant), show.legend = FALSE, alpha = 0.5) + facet_grid(Group ~ `Perturbation Direction`) + theme_minimal_grid() +
  geom_label(mapping = aes(x = 0, y = Vm, color = Participant, label = Participant), data = taRNorm, show.legend = FALSE)
p
```
